---
output:
  html_document:
    toc: no
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dplyr)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Global Variables, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y))

```


```{r Establish Connection, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")


# Connection to Clarity Tables -------------------------------------------------
slot_raw_tbl <- tbl(conn2, "Y_DM_BOOKED_FILLED_RATE")
access_raw_tbl <- tbl(conn2, "MV_DM_PATIENT_ACCESS")
availability_raw_tbl <- tbl(conn2, "V_AVAILABILITY")
block_raw_tbl <- tbl(conn2, "AVAIL_BLOCK")
block_name_tbl <- tbl(conn2, "ZC_APPT_BLOCK")
orders_raw_tbl <- tbl(conn2, "ORDER_PROC")
coverage_tbl <- tbl(conn2, "V_PAT_ENC_COVERAGE")
encounters_tbl <- tbl(conn2, "PAT_ENC")
myChart_tbl <- tbl(conn2, "V_MYC_MESG")
inBasket_tbl <- tbl(conn2, "IB_MESSAGES")
template_tbl <- tbl(conn2, "TEMPLATE")
user_activity_hour_tbl <- tbl(conn2, "UAL_ACTIVITY_HOURS") # User Activity Summary by Hour
user_login_activity_tbl <- tbl(conn2, "V_ACCESS_LOG") # User Log In/Out Time
user_access_log_tbl <- tbl(conn2, "ACCESS_LOG")
clarity_ser_tbl <- tbl(conn2, "CLARITY_SER") # Physician Titles
clarity_lws_tbl <- tbl(conn2, "CLARITY_LWS") # Workstation-Room Mapping
access_workstation_tbl <- tbl(conn2, "ACCESS_WRKF")


# Connection to OAO Tables -----------------------------------------------------
utilization_tbl <-  tbl(conn1, in_schema("VILLEA04", "UTILIZATION_VIEW"))

```


```{r Report Variables, echo = FALSE, warning = FALSE, message = FALSE}

day_order <- c("Mon","Tue","Wed","Thu","Fri","Sat","Sun")
hour_order <- as.vector(seq(7,20))
visit_capacity_order <- c(paste0("visit_capacity_",4:10))

report_run_date <- Sys.Date()

```


```{r Workstation Mapping, echo = FALSE, warning = FALSE, message = FALSE}

workstation_mapping <- read_excel(file.choose(), sheet = 1, col_names = TRUE, col_types = "text", na = "", skip = 0)
workstation_mapping <- workstation_mapping %>% 
  left_join(clarity_lws_tbl %>% 
              dplyr::select(WORKSTATION_ID, WORKSTN_IDENTIFIER, PRIM_DEPARTMENT_ID),
            by = "WORKSTN_IDENTIFIER", 
            na_matches = "never",
            copy = TRUE) %>%
  mutate()


## Join for primary department details -----------------------------------------
workstation_mapping <- workstation_mapping %>%
  mutate(PRIM_DEPARTMENT_ID = as.character(PRIM_DEPARTMENT_ID)) %>%
  left_join(access_raw_tbl %>% 
              mutate(DEPARTMENT_ID = as.character(DEPARTMENT_ID)) %>%
              group_by(DEPARTMENT_ID, SITE) %>%
              summarise(total = n()) %>%
              dplyr::select(-total),
            by = c("PRIM_DEPARTMENT_ID" = "DEPARTMENT_ID"),
            na_matches = "never",
            copy = TRUE) %>%
  rename("PRIM_SITE" = "SITE") 


## Subset mapped workstations only ---------------------------------------------
workstations_mapped <- unique((workstation_mapping %>% filter(!is.na(WORKSTN_IDENTIFIER)))$WORKSTATION_ID)

```


```{r User Activity Data Mapping, echo = FALSE, warning = FALSE, message = FALSE}

## Retreive user activity data for workstations mapped -------------------------
user_activity_hour <- user_activity_hour_tbl %>%
  filter(WORKSTATION_ID %in% workstations_mapped)
 


## Map Provider Type on User ID -----------------------
user_activity_hour <- user_activity_hour %>%
  left_join(clarity_ser_tbl %>%
              dplyr::select(USER_ID, PROV_ID, PROV_NAME, PROV_TYPE) %>%
              rename("PROV_ID_USER" = "PROV_ID",
                     "PROV_TYPE_USER" = "PROV_TYPE",
                     "PROV_NAME_USER" = "PROV_NAME"),
            by = c("USER_ID"),
            copy = TRUE) 


## Map Encounter Details -------------------
user_activity_hour <- user_activity_hour %>%
  left_join(access_raw_tbl %>%
              dplyr::select(PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_ID,
                            SITE, DEPT_SPECIALTY_NAME, LOC_NAME,
                            CONTACT_DATE, DERIVED_STATUS_DESC,
                            CHECKIN_DTTM, ROOMED_DTTM, VISIT_END_DTTM, CHECKOUT_DTTM, CYCLE_TIME_MINUTES, TIME_IN_ROOM_MINUTES,
                            MRN, APPT_DTTM) %>%
              rename("PROV_ID_SCHEDULING" = "PROV_ID"),
            by = c("PAT_ENC_CSN_ID"),
            copy = TRUE)


## Map Provider Type on Scheduled Provider -----------------------
user_activity_hour <- user_activity_hour %>%
  left_join(clarity_ser_tbl %>%
              dplyr::select(PROV_ID, PROV_TYPE) %>%
              rename("PROV_TYPE_SCHEDULING" = "PROV_TYPE"),
            by = c("PROV_ID_SCHEDULING" = "PROV_ID"),
            copy = TRUE) 


## Join by Workstation Mapping ------------------
user_activity_hour_data <- user_activity_hour %>%
   filter(ACTIVITY_HOUR_DTTM >= as.Date("2024-03-01") & 
         ACTIVITY_HOUR_DTTM < as.Date("2024-03-03"))%>%
  collect() 


## Map Workstation Details using Internal Workstation Mapping Data ------------
user_activity_hour_data <- user_activity_hour_data %>%
  left_join(workstation_mapping,
            by = "WORKSTATION_ID",
            na_matches = "never")
            
  
## Flag/Filter activities not representing actual visits in room --------------
user_activity_hour_data <- user_activity_hour_data %>%
  mutate(valid_activity = ifelse(as.Date(ACTIVITY_HOUR_DTTM, "%y-%m-%d") == as.Date(CONTACT_DATE, "%y-%m-%d"), "Yes", "No")) %>%
  mutate(valid_activity = ifelse(is.na(valid_activity), "No", valid_activity)) %>%
  filter(valid_activity == "Yes") 

#writing into csv file
write.csv(user_activity_hour_data, "user_activity_hour_data.csv", row.names = FALSE)


```


```{r Calculate Room Minutes, echo = FALSE, warning = FALSE, message = FALSE}

## Calculate Minutes in Room ----------------------
utilization_data <- user_activity_hour_data %>%
  dplyr::select(ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, PROV_NAME_WID, PROV_TYPE_SCHEDULING, 
                WORKSTN_IDENTIFIER, Room, `Type Name`,
                DEPARTMENT_ID, PRIM_SITE, DEPARTMENT_NAME,
                Campus, `Building Address`, `Floor/Suite`, 
                WORKSTN_OWNER, `Leased or Owned`, `Hospital or NonHospital`,
                NUMBER_OF_SECONDS_ACTIVE_Q1, NUMBER_OF_SECONDS_ACTIVE_Q2, NUMBER_OF_SECONDS_ACTIVE_Q3, NUMBER_OF_SECONDS_ACTIVE_Q4)


## Collapse Active Seconds by Quarter columns into rows --------------------
### Grouping by appointment scheduled provider NOT user ID & unique encounter ID 
utilization_data <- utilization_data %>%
  pivot_longer(NUMBER_OF_SECONDS_ACTIVE_Q1:NUMBER_OF_SECONDS_ACTIVE_Q4,
               names_to = "active_quarter",
               values_to = "active_seconds") %>%
  group_by(ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_TYPE_SCHEDULING, 
           WORKSTN_IDENTIFIER, Room, `Type Name`,
           DEPARTMENT_ID, PRIM_SITE, 
           Campus, `Building Address`, `Floor/Suite`, 
           WORKSTN_OWNER, `Leased or Owned`, `Hospital or NonHospital`,
           active_quarter) %>%
  summarise(active_seconds = sum(active_seconds))


utilization_data <- utilization_data %>%
  mutate(active_quarter= case_when(active_quarter == "NUMBER_OF_SECONDS_ACTIVE_Q1" ~ "Q1",
                                   active_quarter == "NUMBER_OF_SECONDS_ACTIVE_Q2" ~ "Q2",
                                   active_quarter == "NUMBER_OF_SECONDS_ACTIVE_Q3" ~ "Q3",
                                   active_quarter == "NUMBER_OF_SECONDS_ACTIVE_Q4" ~ "Q4",
                                   TRUE ~ ""))


## Calculate Minutes in Room by hour and quarter -----------------------------   
utilization_data <- utilization_data %>%
  arrange(ACTIVITY_HOUR_DTTM, active_quarter) %>%
  arrange(WORKSTN_IDENTIFIER) %>%
  group_by(WORKSTN_IDENTIFIER) %>%
  mutate(unique_id = as.integer(forcats::fct_inorder(as.character(PAT_ENC_CSN_ID)))) %>% # Unique ID based on patient per room
  mutate(quarter_start = case_when(active_quarter == "Q1" ~ ACTIVITY_HOUR_DTTM,
                                   active_quarter == "Q2" ~ ACTIVITY_HOUR_DTTM + 15*60,
                                   active_quarter == "Q3" ~ ACTIVITY_HOUR_DTTM + 30*60,
                                   active_quarter == "Q4" ~ ACTIVITY_HOUR_DTTM + 45*60),
         quarter_end = case_when(active_quarter == "Q1" ~ ACTIVITY_HOUR_DTTM + 14*60,
                                   active_quarter == "Q2" ~ ACTIVITY_HOUR_DTTM + 29*60,
                                   active_quarter == "Q3" ~ ACTIVITY_HOUR_DTTM + 44*60,
                                   active_quarter == "Q4" ~ ACTIVITY_HOUR_DTTM + 59*60))


## Assign 15 minutes to active quarters by hour ------------------------------
### Start and End of quarter by hour, room and encounter ID 
active_minutes <- utilization_data %>%
  mutate(activity_date = as.Date(ACTIVITY_HOUR_DTTM, "%y-%m-%d")) %>%
  group_by(activity_date, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID) %>%
  filter(active_seconds > 0) %>% # Disregard any activities occured for less than 5 seconds
  mutate(pt_room_enter = min(quarter_start),
         pt_room_exit = max(quarter_end)) %>%
  dplyr::select(activity_date, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID, pt_room_enter, pt_room_exit)


### Merge with active_minutes 
utilization_data <- utilization_data %>%
  distinct() %>%
  mutate(activity_date = as.Date(ACTIVITY_HOUR_DTTM, "%y-%m-%d"),
         activity_hour = format(strptime(ACTIVITY_HOUR_DTTM, "%Y-%m-%d %H:%M:%S"), "%H")) %>%
  left_join(active_minutes, 
            by = c("activity_date", "WORKSTN_IDENTIFIER", "PAT_ENC_CSN_ID")) %>%
  distinct() %>%
  mutate(room_minutes = ifelse(between(quarter_start, pt_room_enter, pt_room_exit) == TRUE, 15, 0))
  


## Locate Patient's Primary Room for Turns/Room ------------------------------
### Calculate total room minutes spent per room per patient
utilization_data <- utilization_data %>%
  ungroup() %>%
  arrange(PAT_ENC_CSN_ID, quarter_start) %>%
  group_by(activity_date, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID) %>%
  mutate(total_room_minutes = sum(room_minutes, na.rm = TRUE)) %>% # calculate total room minutes by day, room and patient
  group_by(activity_date, PAT_ENC_CSN_ID) %>%
  mutate(primary_room = ifelse(WORKSTN_IDENTIFIER[which.max(total_room_minutes)] == WORKSTN_IDENTIFIER, 1, 0)) %>% 
  group_by(activity_date, primary_room, PAT_ENC_CSN_ID) %>%
  mutate(first_entered = row_number()) %>%
  mutate(first_entered = ifelse(primary_room == 0, NA,
                                ifelse(room_minutes == 0, NA, first_entered))) %>%
  group_by(activity_date, PAT_ENC_CSN_ID) %>%
  mutate(first_entered = ifelse(first_entered[which.min(first_entered)] == first_entered, 1, NA))

utilization_data <- utilization_data %>%
  ungroup() %>%
  arrange(PAT_ENC_CSN_ID, quarter_start) %>%
  group_by(activity_date, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID) %>%
  mutate(total_room_minutes = sum(room_minutes, na.rm = TRUE)) %>% # calculate total room minutes by day, room and patient
  group_by(activity_date, PAT_ENC_CSN_ID) %>%
  mutate(primary_room = ifelse(WORKSTN_IDENTIFIER[which.max(total_room_minutes)] == WORKSTN_IDENTIFIER, 1, 0)) %>% 
  group_by(activity_date, primary_room, PAT_ENC_CSN_ID) %>%
  mutate(first_entered = row_number()) %>%
  mutate(first_entered = ifelse(primary_room == 0, NA,
                                ifelse(room_minutes == 0, NA, first_entered))) %>%
  group_by(activity_date, PAT_ENC_CSN_ID) %>%
  mutate(first_entered = ifelse(first_entered[which.min(first_entered)] == first_entered, 1, NA))


## creating session column in utilization_data table

utilization_data <- utilization_data %>%
  mutate(session = ifelse(as.numeric(activity_hour) < 12, "AM",
                          ifelse(as.numeric(activity_hour) >= 12 & as.numeric(activity_hour) < 17, "PM", "EVE")))
 

## Calculate Utilization & Turns by Rooom, Date, and Hour --------------------
room_utilization <- utilization_data %>%
  ungroup() %>%
  group_by(Campus, `Building Address`, `Floor/Suite`, 
           DEPARTMENT_ID, PRIM_SITE, DEPARTMENT_NAME, 
           WORKSTN_IDENTIFIER, 
           # Room, `Type Name`, 
           WORKSTN_OWNER, `Leased or Owned`, `Hospital or NonHospital`,
           PROV_NAME_WID, PROV_TYPE_SCHEDULING,
           activity_date, activity_hour, active_quarter, room_minutes) %>%
  summarise(turns = sum(first_entered, na.rm = TRUE)) %>%
  group_by(Campus, `Building Address`, `Floor/Suite`, 
           DEPARTMENT_ID, PRIM_SITE, DEPARTMENT_NAME, 
           WORKSTN_IDENTIFIER, 
           # Room, `Type Name`, 
           WORKSTN_OWNER, `Leased or Owned`, `Hospital or NonHospital`,
           PROV_NAME_WID, PROV_TYPE_SCHEDULING,
           activity_date, activity_hour) %>%
  summarise(room_minutes = sum(room_minutes),
            turns = sum(turns))



## Calculate Total Rooms Assigned per Resource ---------------------------------
room_utilization <- room_utilization %>%
  mutate(session = ifelse(as.numeric(activity_hour) < 12, "AM",
                          ifelse(as.numeric(activity_hour) >= 12 & as.numeric(activity_hour) < 17, "PM", "EVE"))) %>%
  group_by(activity_date, session, PROV_NAME_WID, WORKSTN_IDENTIFIER) %>%
  mutate(total_room_used_session = ifelse(row_number()==1, 1, 0))

#writing into csv file
write.csv(room_utilization, "room_utilization.csv", row.names = FALSE)
  
#writing into csv file
write.csv(utilization_data, "utilization_data.csv", row.names = FALSE)

```


```{r Format Data for Oracle, echo = FALSE, warning = FALSE, message = FALSE}

## Fill in missing dates and hours ------------------------------------------
fill_dates <- room_utilization %>%
  dplyr::select(-c(DEPARTMENT_NAME, PROV_NAME_WID, room_minutes, turns)) %>%
  mutate(value = 1) %>%
  arrange(activity_date) %>%
  pivot_wider(names_from = activity_date,
              values_from =  value,
              values_fill = 0)
fill_dates <- fill_dates %>%
  pivot_longer(16:length(fill_dates),
               names_to = "activity_date",
               values_to = "value")

fill_dates <- fill_dates %>%
  arrange(activity_hour) %>%
  pivot_wider(names_from = activity_hour,
              values_from =  value,
              values_fill = 0)
fill_dates <- fill_dates %>%
  pivot_longer(16:length(fill_dates),
               names_to = "activity_hour",
               values_to = "value") 
fill_dates$value <- NULL


## Merge complete dates/hours data with utilization data --------------------
room_utilization <- left_join(fill_dates, room_utilization %>% mutate(activity_date = as.character(activity_date)))
room_utilization <- room_utilization %>%
  mutate(room_minutes = ifelse(is.na(room_minutes), 0, room_minutes),
         turns = ifelse(is.na(turns), 0, turns))


## Add Activity Year, Year-Month, Day ---------------------------------------
room_utilization <- room_utilization %>%
  mutate(activity_year = format(as.Date(activity_date), "%Y"),
         activity_yearmonth = format(as.Date(activity_date), "%Y-%m"),
         activity_day = format(as.Date(activity_date), "%a"))





# Export a temporary manual file --------------------------------------------
# room_utilization_sample <- room_utilization %>%
#   filter(as.Date(activity_date) >= as.Date("2023-12-01"))
# 
# save(room_utilization_sample, file = "Room Utilization Data Sample.RData")
# 
# require(openxlsx)
# writexl::write_xlsx(room_utilization_subset, "Room Utilization Data Sample.xlsx")
```

```{r Format Data for Oracle, echo = FALSE, warning = FALSE, message = FALSE}

## Calculating Room Assignment Value to calculate avg. rooms assigned per provider

room_assignment <- room_utilization %>%
  group_by(activity_date, session, WORKSTN_IDENTIFIER) %>%
  summarize(num_providers = n_distinct(PROV_NAME_WID)) %>%
  ungroup() %>%
  mutate(room_assignment_value = 1/num_providers)

room_utilization <- room_utilization %>%
  left_join(
    room_assignment %>%
      select(activity_date, session, WORKSTN_IDENTIFIER, room_assignment_value),
    by = c("activity_date", "session", "WORKSTN_IDENTIFIER"),
    copy = TRUE)



```


```{r Format Data for Oracle, echo = FALSE, warning = FALSE, message = FALSE}

## Calculating Room assignment value depanding on unique providers seeing unique patients

room_assignment <- utilization_data %>%
  group_by(activity_date, session, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID) %>%
  distinct(PROV_NAME_WID) %>%
  summarise(collapse_num_providers = paste(PROV_NAME_WID, collapse = ", "))
  

room_assignment <- room_assignment %>%
  group_by(activity_date, session, WORKSTN_IDENTIFIER) %>%
  summarize(num_providers = n_distinct(collapse_num_providers)) %>%
  ungroup() %>%
  mutate(room_assignment_value = 1/num_providers)

room_utilization <- room_utilization %>%
  left_join(
    room_assignment %>%
      select(activity_date, session, WORKSTN_IDENTIFIER, room_assignment_value),
    by = c("activity_date", "session", "WORKSTN_IDENTIFIER"),
    copy = TRUE)


```


```{r Write to Oracle, echo = FALSE, warning = FALSE, message = FALSE}

#Establish Oracle Cloud connection
conn3 <- dbConnect(odbc(), "OAO Cloud DB SoYoun",
                  uid = "KWEONS01",
                  pwd = "wEKMQpqm22*dvM")
 
# ## Write Table in Oracle Database
# dbWriteTable(conn = conn3, name = "Room_Utilization_Table_Test", value = test, row.names = FALSE)
# 
room_util_pull <- tbl(conn3, "ROOM_UTIL_DATA")
room_util_pull_all <- room_util_pull %>%
  collect()

room_util_pull_all <- room_util_pull_all %>%
  distinct()

data_remaining <- anti_join(room_utilization_subset, room_util_pull_all)



# Delete existing data from table in Oracle --------------------------
# dbExecute(conn3, "TRUNCATE TABLE ROOM_UTIL_TEST")


# Write Table to Oracle ----------------------------------------------

batch_size <- 1000

for (i in seq(1, nrow(data_remaining), by = batch_size)) {

batch <- data_remaining[i:(i + batch_size - 1), ]

dbWriteTable(conn = conn3, name = "ROOM_UTIL_DATA", value = batch, row.names = FALSE, append = TRUE)

}


 
batch_size <- 1000
 
index_squence <- seq(1, nrow(monthly_vol), by = batch_size)
 
for (i in index_squence) {
  
  if(i == max(index_squence)) {
    batch <- monthly_vol[i:nrow(monthly_vol), ]
  } else {
    batch <- monthly_vol[i:(i + batch_size - 1), ]
  }
  
  
  #dbWriteTable(conn = conn3, name = "MONTHLY_VOL_DATA", value = batch, row.names = FALSE, append = TRUE)
  
  print(paste0("i is:", i))
  print(batch)
  
}



```

