---
output:
  html_document:
    toc: no
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
  library(glue)
  library(tidyverse)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Establish Connection, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")

```


```{r Report Variables, echo = FALSE, warning = FALSE, message = FALSE}

#day_order <- c("Mon","Tue","Wed","Thu","Fri","Sat","Sun")
#hour_order <- as.vector(seq(7,20))
#visit_capacity_order <- c(paste0("visit_capacity_",4:10))

#report_run_date <- Sys.Date()

```


```{r Workstation Mapping, echo = FALSE, warning = FALSE, message = FALSE}

workstation_drop <- glue("DROP TABLE COMBINED_WORKSTATION_MAPPING")
workstation_query <- glue("CREATE TABLE COMBINED_WORKSTATION_MAPPING AS
                          SELECT a.*, b.WORKSTATION_ID, b.PRIM_DEPARTMENT_ID 
                          FROM
                          ((SELECT * FROM WORKSTATION_MAPPING) a
                          LEFT JOIN (SELECT * FROM CLARITY_LWS) b
                          ON a.WORKSTN_IDENTIFIER = b.WORKSTN_IDENTIFIER)
                          ")


workstation_modified_drop <- glue("DROP TABLE MODIFIED_WORKSTATION_MAPPING")
workstation_modified_query <- glue("CREATE TABLE MODIFIED_WORKSTATION_MAPPING AS
                                    SELECT a.*, b.SITE AS PRIM_SITE, b.PRIM_DEPARTMENT_NAME
                                    FROM COMBINED_WORKSTATION_MAPPING a
                                    LEFT JOIN 
                                    (SELECT CAST(DEPARTMENT_ID AS VARCHAR(255)) AS DEPARTMENT_ID, SITE, DEPARTMENT_NAME AS PRIM_DEPARTMENT_NAME
                                    FROM MV_DM_PATIENT_ACCESS 
                                    GROUP BY DEPARTMENT_ID, SITE, DEPARTMENT_NAME) b
                                    ON CAST(a.PRIM_DEPARTMENT_ID AS VARCHAR(255)) = b.DEPARTMENT_ID
                                   ")

workstation_mapping_subset_drop <- glue("DROP TABLE WORKSTATION_MAPPING_SUBSET")
workstation_mapping_subset_query <- glue("CREATE TABLE WORKSTATION_MAPPING_SUBSET AS
                                         SELECT DISTINCT WORKSTATION_ID
                                         FROM MODIFIED_WORKSTATION_MAPPING
                                         WHERE WORKSTN_IDENTIFIER IS NOT NULL")

```


```{r User Activity Data Mapping, echo = FALSE, warning = FALSE, message = FALSE}

## Retreive user activity data for workstations mapped -------------------------
## Map Provider Type on User ID -----------------------
## Flag/Filter activities not representing actual visits in room --------------


user_activity_drop <- glue("DROP TABLE USER_ACTIVITY_HOUR_TABLE")
user_activity_query <- glue("CREATE TABLE USER_ACTIVITY_HOUR_TABLE AS
                            SELECT i.*, j.CAMPUS, j.BUILDING_ADDRESS, j.FLOOR_SUITE, j.ROOM, j.DEPT_NO,
                            j.WORKSTN_IDENTIFIER, j.TYPE_NAME, j.WORKSTN_OWNER, j.LEASED_OR_OWNED, j.HOSPITAL_OR_NONHOSPITAL,
                            j.PRIM_DEPARTMENT_ID, j.PRIM_DEPARTMENT_NAME, j.PRIM_SITE, 
                            CASE WHEN TO_CHAR(i.ACTIVITY_HOUR_DTTM, 'YYYY-MM-DD') = TO_CHAR(i.CONTACT_DATE, 'YYYY-MM-DD') THEN 'Yes' ELSE 'No' END AS VALID_ACTIVITY
                            FROM
                            (SELECT g.*, h.PROV_TYPE_SCHEDULING
                            FROM
                            (SELECT e.*, f.DEPARTMENT_ID, f.DEPARTMENT_NAME, f.PROV_NAME_WID, f.PROV_ID_SCHEDULING, f.SITE, 
                            f.DEPT_SPECIALTY_NAME, f.LOC_NAME, f.CONTACT_DATE, f.DERIVED_STATUS_DESC, f.CHECKIN_DTTM, f.ROOMED_DTTM, f.VISIT_END_DTTM,
                            f.CHECKOUT_DTTM, f.CYCLE_TIME_MINUTES, f.TIME_IN_ROOM_MINUTES, f.MRN, f.APPT_DTTM
                            FROM
                            (SELECT c.*, d.PROV_ID_USER, d.PROV_TYPE_USER, d.PROV_NAME_USER
                            FROM
                            (SELECT a.* FROM 
                            ((SELECT * FROM UAL_ACTIVITY_HOURS WHERE TO_CHAR(ACTIVITY_HOUR_DTTM,'YYYY-MM-DD') = '2024-03-03') a
                            INNER JOIN (SELECT * FROM WORKSTATION_MAPPING_SUBSET) b
                            ON a.WORKSTATION_ID = b.WORKSTATION_ID)) c
                            LEFT JOIN 
                            (SELECT USER_ID, PROV_ID AS PROV_ID_USER, PROV_NAME AS PROV_NAME_USER, PROV_TYPE AS PROV_TYPE_USER FROM CLARITY_SER) d
                            ON c.USER_ID = d.USER_ID) e
                            LEFT JOIN 
                            (SELECT PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_ID AS PROV_ID_SCHEDULING,
                            SITE, DEPT_SPECIALTY_NAME, LOC_NAME, CONTACT_DATE, DERIVED_STATUS_DESC,
                            CHECKIN_DTTM, ROOMED_DTTM, VISIT_END_DTTM, CHECKOUT_DTTM, CYCLE_TIME_MINUTES, TIME_IN_ROOM_MINUTES,
                            MRN, APPT_DTTM
                            FROM MV_DM_PATIENT_ACCESS) f
                            ON e.PAT_ENC_CSN_ID = f.PAT_ENC_CSN_ID) g
                            LEFT JOIN 
                            (SELECT PROV_ID, PROV_TYPE AS PROV_TYPE_SCHEDULING FROM CLARITY_SER) h
                            ON g.PROV_ID_SCHEDULING = h.PROV_ID) i
                            LEFT JOIN 
                            (SELECT CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, ROOM, DEPT_NO,
                            WORKSTN_IDENTIFIER, TYPE_NAME, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,
                            WORKSTATION_ID, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE 
                            FROM MODIFIED_WORKSTATION_MAPPING) j
                            ON i.WORKSTATION_ID = j.WORKSTATION_ID
                            WHERE CASE WHEN TO_CHAR(i.ACTIVITY_HOUR_DTTM, 'YYYY-MM-DD') = TO_CHAR(i.CONTACT_DATE, 'YYYY-MM-DD') THEN 'Yes' ELSE 'No' END = 'Yes'
                            ")


user_activity_drop_test <- glue("DROP TABLE USER_ACTIVITY_HOUR_TABLE_TEST")
user_activity_query_test <- glue("CREATE TABLE USER_ACTIVITY_HOUR_TABLE_TEST AS
                            SELECT i.*, j.CAMPUS, j.BUILDING_ADDRESS, j.FLOOR_SUITE, j.ROOM, j.DEPT_NO,
                            j.WORKSTN_IDENTIFIER, j.TYPE_NAME, j.WORKSTN_OWNER, j.LEASED_OR_OWNED, j.HOSPITAL_OR_NONHOSPITAL,
                            j.PRIM_DEPARTMENT_ID, j.PRIM_DEPARTMENT_NAME, j.PRIM_SITE, 
                            CASE WHEN TO_CHAR(i.ACTIVITY_HOUR_DTTM, 'YYYY-MM-DD') = TO_CHAR(i.CONTACT_DATE, 'YYYY-MM-DD') THEN 'Yes' ELSE 'No' END AS VALID_ACTIVITY
                            FROM
                            (SELECT g.*, h.PROV_TYPE_SCHEDULING
                            FROM
                            (SELECT e.*, f.DEPARTMENT_ID, f.DEPARTMENT_NAME, f.PROV_NAME_WID, f.PROV_ID_SCHEDULING, f.SITE, 
                            f.DEPT_SPECIALTY_NAME, f.LOC_NAME, f.CONTACT_DATE, f.DERIVED_STATUS_DESC, f.CHECKIN_DTTM, f.ROOMED_DTTM, f.VISIT_END_DTTM,
                            f.CHECKOUT_DTTM, f.CYCLE_TIME_MINUTES, f.TIME_IN_ROOM_MINUTES, f.MRN, f.APPT_DTTM
                            FROM
                            (SELECT c.*, d.PROV_ID_USER, d.PROV_TYPE_USER, d.PROV_NAME_USER
                            FROM
                            (SELECT a.* FROM 
                            ((SELECT * FROM UAL_ACTIVITY_HOURS WHERE TO_CHAR(ACTIVITY_HOUR_DTTM,'YYYY-MM-DD') >= '2024-03-01' AND 
                            TO_CHAR(ACTIVITY_HOUR_DTTM,'YYYY-MM-DD') <= '2024-03-02') a 
                            INNER JOIN (SELECT * FROM WORKSTATION_MAPPING_SUBSET) b
                            ON a.WORKSTATION_ID = b.WORKSTATION_ID)) c
                            LEFT JOIN 
                            (SELECT USER_ID, PROV_ID AS PROV_ID_USER, PROV_NAME AS PROV_NAME_USER, PROV_TYPE AS PROV_TYPE_USER FROM CLARITY_SER) d
                            ON c.USER_ID = d.USER_ID) e
                            LEFT JOIN 
                            (SELECT PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_ID AS PROV_ID_SCHEDULING,
                            SITE, DEPT_SPECIALTY_NAME, LOC_NAME, CONTACT_DATE, DERIVED_STATUS_DESC,
                            CHECKIN_DTTM, ROOMED_DTTM, VISIT_END_DTTM, CHECKOUT_DTTM, CYCLE_TIME_MINUTES, TIME_IN_ROOM_MINUTES,
                            MRN, APPT_DTTM
                            FROM MV_DM_PATIENT_ACCESS) f
                            ON e.PAT_ENC_CSN_ID = f.PAT_ENC_CSN_ID) g
                            LEFT JOIN 
                            (SELECT PROV_ID, PROV_TYPE AS PROV_TYPE_SCHEDULING FROM CLARITY_SER) h
                            ON g.PROV_ID_SCHEDULING = h.PROV_ID) i
                            LEFT JOIN 
                            (SELECT CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, ROOM, DEPT_NO,
                            WORKSTN_IDENTIFIER, TYPE_NAME, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,
                            WORKSTATION_ID, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE 
                            FROM MODIFIED_WORKSTATION_MAPPING) j
                            ON i.WORKSTATION_ID = j.WORKSTATION_ID
                            WHERE CASE WHEN TO_CHAR(i.ACTIVITY_HOUR_DTTM, 'YYYY-MM-DD') = TO_CHAR(i.CONTACT_DATE, 'YYYY-MM-DD') THEN 'Yes' ELSE 'No' END = 'Yes'
                            ")


```


```{r Calculate Room Minutes, echo = FALSE, warning = FALSE, message = FALSE}

## Calculate Minutes in Room ----------------------
utilization_drop <- glue("DROP TABLE UTILIZATION_TABLE")
utilization_query <- glue("CREATE TABLE UTILIZATION_TABLE AS
                           SELECT a.*, DENSE_RANK() OVER (PARTITION BY WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID ORDER BY ACTIVITY_HOUR_DTTM) AS UNIQUE_ID,
                           CASE 
                           WHEN ACTIVE_QUARTER = 'Q1' THEN ACTIVITY_HOUR_DTTM
                           WHEN ACTIVE_QUARTER = 'Q2' THEN ACTIVITY_HOUR_DTTM + 15*60
                           WHEN ACTIVE_QUARTER = 'Q3' THEN ACTIVITY_HOUR_DTTM + 30*60
                           WHEN ACTIVE_QUARTER = 'Q4' THEN ACTIVITY_HOUR_DTTM + 45*60
                           ELSE NULL
                           END AS QUARTER_START,
                           CASE 
                           WHEN ACTIVE_QUARTER = 'Q1' THEN ACTIVITY_HOUR_DTTM + 14*60
                           WHEN ACTIVE_QUARTER = 'Q2' THEN ACTIVITY_HOUR_DTTM + 29*60
                           WHEN ACTIVE_QUARTER = 'Q3' THEN ACTIVITY_HOUR_DTTM + 44*60
                           WHEN ACTIVE_QUARTER = 'Q4' THEN ACTIVITY_HOUR_DTTM + 59*60
                           ELSE NULL
                           END AS QUARTER_END
                           FROM
                           (SELECT ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_TYPE_SCHEDULING,
                           WORKSTN_IDENTIFIER, ROOM, TYPE_NAME, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE,
                           CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,
                           ACTIVE_QUARTER, SUM(ACTIVE_SECONDS) AS ACTIVE_SECONDS
                           FROM
                           (
                           SELECT ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_TYPE_SCHEDULING,
                           WORKSTN_IDENTIFIER, ROOM, TYPE_NAME, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE,
                           CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,
                           'Q1' AS ACTIVE_QUARTER, NUMBER_OF_SECONDS_ACTIVE_Q1 AS ACTIVE_SECONDS
                           FROM USER_ACTIVITY_HOUR_TABLE
                           UNION ALL
                           SELECT ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_TYPE_SCHEDULING,
                           WORKSTN_IDENTIFIER, ROOM, TYPE_NAME, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE,
                           CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,                           
                           'Q2' AS ACTIVE_QUARTER, NUMBER_OF_SECONDS_ACTIVE_Q2 AS ACTIVE_SECONDS
                           FROM USER_ACTIVITY_HOUR_TABLE
                           UNION ALL
                           SELECT ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_TYPE_SCHEDULING,
                           WORKSTN_IDENTIFIER, ROOM, TYPE_NAME, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE,
                           CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,
                           'Q3' AS ACTIVE_QUARTER, NUMBER_OF_SECONDS_ACTIVE_Q3 AS ACTIVE_SECONDS
                           FROM USER_ACTIVITY_HOUR_TABLE
                           UNION ALL
                           SELECT ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_TYPE_SCHEDULING,
                           WORKSTN_IDENTIFIER, ROOM, TYPE_NAME, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE,
                           CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,
                           'Q4' AS ACTIVE_QUARTER, NUMBER_OF_SECONDS_ACTIVE_Q4 AS ACTIVE_SECONDS
                           FROM USER_ACTIVITY_HOUR_TABLE
                           )
                           GROUP BY 
                           ACTIVITY_HOUR_DTTM, PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID, PROV_TYPE_SCHEDULING,
                           WORKSTN_IDENTIFIER, ROOM, TYPE_NAME, PRIM_DEPARTMENT_ID, PRIM_DEPARTMENT_NAME, PRIM_SITE,
                           CAMPUS, BUILDING_ADDRESS, FLOOR_SUITE, WORKSTN_OWNER, LEASED_OR_OWNED, HOSPITAL_OR_NONHOSPITAL,
                           ACTIVE_QUARTER) a
                           ORDER BY ACTIVITY_HOUR_DTTM, ACTIVE_QUARTER, WORKSTN_IDENTIFIER
                          ")


## Assign 15 minutes to active quarters by hour ------------------------------
### Start and End of quarter by hour, room and encounter ID 
active_minutes_drop <- glue("DROP TABLE ACTIVE_MINUTES")
active_minutes_query <- glue("CREATE TABLE ACTIVE_MINUTES AS
                            SELECT TO_CHAR(ACTIVITY_HOUR_DTTM,'YYYY-MM-DD') AS ACTIVITY_DATE, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID, 
                            MIN(QUARTER_START) AS PT_ROOM_ENTER, MAX(QUARTER_END) AS PT_ROOM_EXIT
                            FROM UTILIZATION_TABLE
                            WHERE ACTIVE_SECONDS>0
                            GROUP BY TO_CHAR(ACTIVITY_HOUR_DTTM,'YYYY-MM-DD'), WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID
                            ")



### Merge with active_minutes_table
merged_utilization_drop <- glue("DROP TABLE MERGED_UTILIZATION_TABLE")
merged_utilization_query <- glue("CREATE TABLE MERGED_UTILIZATION_TABLE AS
                                     SELECT DISTINCT d.*,
                                     CASE WHEN QUARTER_START BETWEEN PT_ROOM_ENTER AND PT_ROOM_EXIT THEN 15 ELSE 0 END AS ROOM_MINUTES
                                     FROM
                                     (SELECT c.*, b.PT_ROOM_ENTER, PT_ROOM_EXIT
                                     FROM
                                     (SELECT a.*, 
                                     TO_CHAR(ACTIVITY_HOUR_DTTM, 'YYYY-MM-DD') AS ACTIVITY_DATE, 
                                     TO_CHAR(ACTIVITY_HOUR_DTTM, 'HH24') AS ACTIVITY_HOUR
                                     FROM (SELECT DISTINCT * FROM UTILIZATION_TABLE) a) c
                                     LEFT JOIN (SELECT * FROM ACTIVE_MINUTES) b
                                     ON c.ACTIVITY_DATE = b.ACTIVITY_DATE AND 
                                     c.WORKSTN_IDENTIFIER = b.WORKSTN_IDENTIFIER AND
                                     c.PAT_ENC_CSN_ID = b.PAT_ENC_CSN_ID) d
                                    ")



## Locate Patient's Primary Room for Turns/Room ------------------------------
### Calculate total room minutes spent per room per patient

processed_utilization_drop <- glue("DROP TABLE PROCESSED_UTILIZATION_TABLE")
processed_utilization_query <-glue("CREATE TABLE PROCESSED_UTILIZATION_TABLE AS
                                   WITH TOTALROOMMINUTES AS (
                                   SELECT ACTIVITY_DATE, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID, SUM(ROOM_MINUTES) AS TOTAL_ROOM_MINUTES
                                   FROM MERGED_UTILIZATION_TABLE
                                   GROUP BY ACTIVITY_DATE, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID
                                   ),
                                   PRIMARYROOM AS (
                                   SELECT ACTIVITY_DATE, PAT_ENC_CSN_ID,
                                   CASE WHEN MAX(TOTAL_ROOM_MINUTES) OVER PARTITION BY ACTIVITY_DATE, PAT_ENC_CSN_ID) = TOTAL_ROOM_MINUTES THEN 1 ELSE 0 END AS PRIMARY_ROOM
                                   FROM TOTALROOMMINUTES
                                   ),
                                   FIRSTENTERED AS (
                                   SELECT ACTIVITY_DATE, PAT_ENC_CSN_ID,
                                   ROW_NUMBER() OVER (PARTITION BY ACTIVITY_DATE, PAT_ENC_CSN_ID ORDER BY PAT_ENC_CSN_ID) AS FIRST_ENTERED
                                   FROM MERGED_UTILIZATION_DATA
                                   )
                                   SELECT u.*, p.PRIMARY_ROOM,
                                   CASE WHEN f.FIRST_ENTERED = 1 THEN 1 ELSE NULL END AS FIRST_ENTERED
                                   FROM MERGED_UTILIZATION_DATA u
                                   JOIN PRIMARYROOM p on u.ACTIVITY_DATE = p.ACTIVITY_DATE AND u.PAT_ENC_CSN_ID = p.PAT_ENC_CSN_ID
                                   JOIN FIRSTENTERED f on u.ACTIVITY_DATE = f.ACTIVITY_DATE AND u.PAT_ENC_CSN_ID = f.PAT_ENC_CSN_ID
                                   ")

### to be continued here
  
```


```{r Room Assignment Value, echo = FALSE, warning = FALSE, message = FALSE}

## Calculating Room assignment value depanding on unique providers seeing unique patients
room_assignment_drop <- glue("DROP TABLE ROOM_ASSIGNMENT_TABLE")
room_assignment_query <- glue("CREATE TABLE ROOM_ASSIGNMENT_TABLE AS
                              SELECT ACTIVITY_DATE, SESSION, WORKSTN_IDENTIFIER, 1/COUNT(DISTINCT COLLAPSE_NUM_PROVIDERS) AS ROOM_ASSIGNMENT_VALUE
                              FROM
                              (SELECT ACTIVITY_DATE, SESSION, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID, 
                              GROUP_CONCAT(DISTINCT PROV_NAME_WID,',') AS COLLAPSE_NUM_PROVIDERS
                              FROM UTILIZATION_DATA
                              GROUP BY ACTIVITY_DATE, SESSION, WORKSTN_IDENTIFIER, PAT_ENC_CSN_ID)
                              GROUP BY ACTIVITY_DATE, SESSION, WORKSTN_IDENTIFIER
                             ")

## merging with room_utilization_table
room_util_merged_drop <- glue("DROP TABLE ROOM_UTILIZATION_MERGED")
room_util_merged_query <- glue("CREATE TABLE ROOM_UTILIZATION_MERGED AS
                                SELECT a.*, b.ROOM_ASSIGNMENT_VALUE
                                (SELECT * FROM ROOM_UTILIZATION_TABLE) a
                                LEFT JOIN
                                (SELECT ACTIVITY_DATE, SESSION, WORKSTN_IDENTIFIER, ROOM_ASSIGNMENT_VALUE
                                FROM ROOM_ASSIGNMENT TABLE) b
                               ON a.ACTIVITY_DATE = b.ACTIVITY_DATE AND
                                  a.SESSION = b.SESSION AND
                                  a.WORKSTN_IDENTIFIER = b.WORKSTN_IDENTIFIER
                               ")

```


```{r Room Assignment Value, echo = FALSE, warning = FALSE, message = FALSE}

## updating workstation owner based on moving workstations and their start and end dates

updated_workstn_owner_drop <- glue("DROP TABLE PROD_ROOM_UTILIZATION_TABLE")
updated_workstn_owner_query <- glue("CREATE TABLE PROD_ROOM_UTILIZATION_TABLE AS
                               SELECT a.CAMPUS,
                               a.BUILDING_ADDRESS,
                               a.FLOOR_SUITE,
                               a.DEPARTMENT_ID,
                               a.PRIM_SITE,
                               a.DEPARTMENT_NAME,
                               a.WORKSTN_IDENTIFIER,
                               a.LEASED_OR_OWNED,
                               a.HOSPITAL_OR_NONHOSPITAL,
                               a.PROV_NAME_WID,
                               a.PROV_TYPE_SCHEDULING,
                               a.ACTIVITY_DATE,
                               a.ACTIVITY_HOUR,
                               a.TURNS_PRIMARY_ROOM,
                               a.TURNS_ALL_ROOMS,
                               a.ROOM_MINUTES,
                               a.SESSION_TYPE,
                               a.TOTAL_ROOM_USED_SESSION,
                               a.ROOM_ASSIGNMENT_VALUE,
                               a.ROOM,
                               a.ROOM_TYPE,
                               a.VISIT_METHOD,
                               a.VISIT_TYPE,
                               b.WORKSTN_OWNER
                               FROM
                              (SELECT * FROM ROOM_UTILIZATION_TABLE) a
                               LEFT JOIN 
                              (SELECT WORKSTN_IDENTIFIER, WORKSTN_OWNER, START_DATE, END_DATE FROM TEMP_WORKSTATION_MAPPING) b
                               ON a.WORKSTN_IDENTIFIER = b.WORKSTN_IDENTIFIER
                               AND EXTRACT(MONTH FROM a.ACTIVITY_DATE) >= EXTRACT(MONTH FROM b.START_DATE)
                               AND EXTRACT(YEAR FROM a.ACTIVITY_DATE) >= EXTRACT(YEAR FROM b.START_DATE)
                               AND EXTRACT(MONTH FROM a.ACTIVITY_DATE) <= EXTRACT(MONTH FROM b.END_DATE)
                               AND EXTRACT(YEAR FROM a.ACTIVITY_DATE) <= EXTRACT(YEAR FROM b.END_DATE);
                              ")

```


```{r Write to Oracle, echo = FALSE, warning = FALSE, message = FALSE}

## Grouped Table execution
tryCatch({
  conn1 <- dbConnect(drv = odbc(), "OAO Cloud DB SoYoun", timeout = 30)
  dbBegin(conn1)
#  if(dbExistsTable(conn1, "COMBINED_WORKSTATION_MAPPING")){
#  dbExecute(conn1, workstation_drop) 
#  }
#  dbExecute(conn1, workstation_query) 
#  if(dbExistsTable(conn1, "MODIFIED_WORKSTATION_MAPPING")){
#    dbExecute(conn1, workstation_modified_drop) 
#  }
#  dbExecute(conn1, workstation_modified_query) 
#  if(dbExistsTable(conn1, "WORKSTATION_MAPPING_SUBSET")){
#    dbExecute(conn1, workstation_mapping_subset_drop) 
#  }
#    dbExecute(conn1, workstation_mapping_subset_query) 
#   if(dbExistsTable(conn1, "USER_ACTIVITY_HOUR_TABLE")){
#     dbExecute(conn1, user_activity_drop) 
#   }
#   dbExecute(conn1, user_activity_query)  
#   if(dbExistsTable(conn1, "USER_ACTIVITY_HOUR_TABLE_TEST")){
#     dbExecute(conn1, user_activity_drop_test) 
#   }
#   dbExecute(conn1, user_activity_query_test)    
#   if(dbExistsTable(conn1, "UTILIZATION_TABLE")){
#    dbExecute(conn1, utilization_drop) 
#   }
#   dbExecute(conn1, utilization_query) 
#   if(dbExistsTable(conn1, "ACTIVE_MINUTES")){
#    dbExecute(conn1, active_minutes_drop) 
#   }
#   dbExecute(conn1, active_minutes_query)    
#   if(dbExistsTable(conn1, "MERGED_UTILIZATION_TABLE")){
#     dbExecute(conn1, merged_utilization_drop) 
#   }
#   dbExecute(conn1, merged_utilization_query)   
   if(dbExistsTable(conn1, "PROCESSED_UTILIZATION_TABLE")){
     dbExecute(conn1, processed_utilization_drop) 
   }
   dbExecute(conn1, processed_utilization_query) 
     
  dbCommit(conn1)
  dbDisconnect(conn1)
  print("success")
  
},
error = function(err){
  print(paste("Error staging:", err$message))
  dbRollback(conn1)
  dbDisconnect(conn1)
})


```

